D3064R0: Bringing the Laws of Physics to Bear on the OOTA Problem

### 2024-01-11 ootavacuous.tex
Add conditional-multiplication non-trivial sdep example
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-mult-1.litmus @@
\caption{OOTA Multiplication Example, Initial Value 1}
\label{lst:OOTA Multiplication Example, Initial Value of One}
\end{listing}

In contrast, consider
Listing~\ref{lst:OOTA Multiplication Example, Initial Value of One},
which differs from
Listing~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
only in the initial values (1 instead of 0) and the \co{exists}
clause (0 instead of 1).

Because the values loaded from \co{x} and \co{y} on lines~9 and~10
are non-zero, changes to either \co{x} or \co{y} will affect the
value stored to \co{z} by line~11.
There is therefore a separate semantic dependency from the load from
\co{x} to the store to \co{z} and from the load from \co{y} to the store
to \co{z}, which matches typical definitions of semantic dependency.
Yet
Listing~\ref{lst:OOTA Multiplication Example, Initial Value of One}
and
Listing~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
can be thought of as being merely two different executions of the same
program.

>>>>

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-mult-0-cond.litmus @@
\caption{OOTA Conditional Multiplication Example, Initial Value Zero}
\label{lst:OOTA Conditional Multiplication Example, Initial Value Zero}
\end{listing}

For further evidence that there is no semantic dependency from \co{y}
to \co{z} when \co{x} is zero, see the equivalent\footnote{
	But equivalent only because the atomics are all non-volatile!}
program shown in
Listing~\ref{lst:OOTA Conditional Multiplication Example, Initial Value Zero}.
Here, there is not even a load from \co{y} when \co{x} is zero, so there
cannot possibly be a semantic dependency involving this non-existent load.
A similar transformation would load \co{x} only if \co{y} was non-zero,
emphasizing the lack of any semantic dependency between \co{x} and \co{y}.

In both
Listings~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and~\ref{lst:OOTA Conditional Multiplication Example, Initial Value Zero},
an OOTA cycle would need to affect both the \co{x} and the \co{y} branches
of this compound semantic dependency.

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-mult-1.litmus @@
\caption{OOTA Multiplication Example, Initial Value 1}
\label{lst:OOTA Multiplication Example, Initial Value 1}
\end{listing}

In contrast, consider
Listing~\ref{lst:OOTA Multiplication Example, Initial Value 1},
which differs from
Listing~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
only in the initial values (1 instead of 0) and the \co{exists}
clause (0 instead of 1).

Because the values loaded from \co{x} and \co{y} on lines~9 and~10
are non-zero, changes to either \co{x} or \co{y} will affect the
value stored to \co{z} by line~11.
There is therefore a separate semantic dependency from the load from
\co{x} to the store to \co{z} and from the load from \co{y} to the store
to \co{z}, which matches typical definitions of semantic dependency.
Further
Yet
Listing~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and
Listing~\ref{lst:OOTA Multiplication Example, Initial Value 1}
are merely two different executions of the same program.
